---
title: "q3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# Returns TRUE if the (character string) is a lower-case vowel
# (a, e, i, o, or u), or FALSE otherwise.
isLowerVowel = function(letter) {
  if (letter=="a"|letter=="e"|letter=="i"|letter=="o"|letter=="u"){return(TRUE)}
    else{
      return(FALSE)
    }
    
}


isLowerVowel("e")
```


```{r}

# Returns the smaller of x and y (both scalars).
baby.min = function(x, y) {

  if (x>y){return(y)}
  else{return(x)}
}


```


```{r}

#Use an if ... else if ... else statement to complete the following function:

# Given a nonnegative integer, age, returns a character string,
# one of "child" (0-14 years), "youth" (15-24 years),
# "adult" (25-64 years) or "senior" (65 or older).
ageCategory = function(age) {
  if(age<=14){return("child")}
  if(age<=24 & age>=15){return("youth")}
  if(age<=64 & 25<=age){return("adult")}
  else{return("senior")}
  

}

ageCategory(24)
```


```{r}
baby.min.vector = function(x, y) {
ifelse(x<y,x,y)
}

baby.min.vector(2,3)
```

baby.sapply(X=c(1, 4, 9), FUN=sqrt)



```{r}
# For numeric vector X and function FUN, baby.sapply(X, FUN)
# returns a vector whose ith value is FUN(X[i]).
# e.g. baby.sapply(X=c(1, 4, 9), FUN=sqrt) finds
# c(sqrt(1), sqrt(4), sqrt(9))
# and returns
# c(1, 2, 3).
#
# Note: This is a small version of R's built-in function sapply(), which
# applies FUN to each element of X. We'll study sapply() later.
baby.sapply = function(X, FUN) {
for(i in 0:length(X))
 {X[i]=FUN(X[i])
  }
return(X)}



```



# For numeric vector X, factor INDEX, and function FUN that returns
# a single number, baby.tapply(X, INDEX, FUN) applies FUN to a subset of X
# for each level in in INDEX (having the same length as X), returning a
# vector of length(levels(factor(INDEX))) values.
# e.g. baby.tapply(X=mtcars$mpg, INDEX=mtcars$cyl, FUN=mean)
# gives a vector of three means, one each for 4-, 6-, and 8-cylinder cars.
#
# Note: This is a small version of R's function tapply(), which we'll study later.
```{r}

baby.tapply = function(X, INDEX, FUN)
 { v=levels(factor(INDEX))
  for(i in 0:length(v)){
   v[i]=FUN(X[factor(INDEX)==v[i]])
    
    
  }
return(as.integer(v) )
}

baby.tapply(X=mtcars$mpg, INDEX=mtcars$cyl, FUN=mean)
length(levels(factor(mtcars$cyl)))
```


```{r}
# Returns the sum of the even numbers in vector x.
# e.g. sumEven(c(2, 5, 10, 11)) returns 12.
sumEven = function(x) {
return(sum(x[(x%%2==0)]))

  }
sumEven(c(2, 5, 10, 11))
```


```{r}
# Returns the sum of the even numbers in vector x.
sumEven = function(x) {
  k=0
  if (length(x)==0){return(k=0)}
  else{
  for(i in 1:length(x)){
  
  if (x[i]%%2==0 ){k=k+x[i]}
  }
  return(k)}
}

sumEven(c())
```

```{r}
# Returns index of first occurrence of target in x, or 0 if target is not in x.
# e.g. For x = c(8, 7, 6),
# linearSearch(x=x, target=7) returns 2,
# linearSearch(x=x, target=5) returns 0, and
# linearSearch(x=NULL, target=5) returns 0.
linearSearch = function(x, target) {
  if (length(x)==0){return(k=0)}
  else{
  for(i in 1:length(x)){
    if (x[i]==target){return(i)}
    
  }
return(0)}
}



x = c(8, 7, 6)
linearSearch(x=x, target=7) 
linearSearch(x=x, target=5) 
linearSearch(x=NULL, target=5) 
```




```{r}
# Uses binary search to return the index of an occurrence of target in x,
# where x is a vector sorted in increasing order, or 0 if target is not in x.
binarySearch = function(x, target) {
  low <- 1
  high <- length(x)

  while(low <= high) {
    mid <- median(low,high)
    if(x[mid] == target) {
      return(mid)} 
    if(target < x[mid]) 
      {
      high <- mid -1
    } else {
      low  <- mid +1
    }
  }
}

x = c(1,2,3,5,6,7,8,9)

binarySearch(x,7)
```















